A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
5d-4d intro edits

\pagestyle{intro}
\section*{Introduction} 
\label{sect:intro}
\addcontentsline{toc}{section}{Introduction}

@@

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}. In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

@@

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} Super Yang--Mills theory in 8 dimensions admits three classes of twists.  The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
 \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The holomorphic twist also admits a deformation to a topological twist defined on $\spin(7)$-manifolds. This theory is perturbatively trivial, in the sense that the classical BV complex is contractible. It was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}. The partition function of this theory counts $\spin(7)$-instantons modulo gauge \cite{Lewis,DonaldsonThomas,ReyesCarrion}. If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
 \[F = \ast (\Omega\wedge F).\]
\end{itemize}

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang--Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.  The minimal twist, by a pure spinor, is equivalent to a generalized version of the BF theory defined on a product of a complex 3-fold and a real 1-manifold.
 \item \emph{$\mc N=1$ intermediate twist.} The minimal twist admits a deformation to a twist by a rank 1 impure spinor. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau surface and a real oriented 3-manifold. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The minimal twist also admits a deformation to a topological twist defined on $G_2$-manifolds. This theory is again perturbatively trivial. It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}. The partition function of this theory counts $G_2$-monopoles modulo gauge \cite{DonaldsonSegal}. If we denote by $\psi$ the calibration 4-form on a $G_2$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying
\[d_A\sigma = \ast(F_A\wedge \psi).\] 
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model). In general, this theory is only $\ZZ/2\ZZ$-graded. If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/\fg$. 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$. This twist is also calculated in the forthcoming work of Dylan Butson \cite{Butson}.
 \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists. The one by a supercharge of rank $(2, 2)$ is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau curve and a real oriented 4-manifold. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} The other intermediate twist, by a rank $(1, 1)$ supercharge, is equivalent to a generalized form of the BF theory defined on a product of a complex surface and a real surface.
 \item \emph{$\mc N=(1,1)$ topological twist.} The special rank $(1, 1)$ twist admits a deformation to a topological twist defined on Calabi--Yau 3-folds. This theory is perturbatively trivial. It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}. The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}. If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
\begin{align*}
F_{0, 2} + \ol\dd^*_A u &= 0 \\
\Lambda F_{1, 1}\wedge \omega^2 + [u, \bar{u}] + \lambda \omega^3 &= 0.
\end{align*}
\pavel{$\lambda$ to be explained.}
\end{itemize}

\textbf{Dimension 5}
\begin{itemize}
 \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.  This twist is equivalent to a generalized form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.  It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).  This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.  If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized BF theory valued in the adjoint quotient $\gg/\gg$.
 \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist with four invariant directions.  This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.  It is invariant for the group $\spin(2;\RR) \times \spin(3;\RR)$ and can be defined on the product of a 2-manifold and a 3-manifold, each equipped with a spin structure.  This twist was considered in \cite{ElliottPestun} on manifolds of the form $\Sigma \times C \times S^1$, where $\Sigma$ and $C$ are Riemann surfaces, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
 \item \emph{$\mc N=2$ topological A twist.} There are two topological twists in 5d $\mc N=2$.  One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1,1)$ super Yang-Mills theory.  It is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the intermediate twist.  The full family is invariant for the group $\Spin(3;\RR)$.  This theory was studied by Qiu and Zabzine, \cite{QiuZabzine}, where the equations of motion were shown to include the Haydys-Witten equations.  Twisting homomorphisms in this situation were previously studied by Anderson \cite{Anderson}.
 \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with 5d Chern-Simons theory.  This theory is only $\ZZ/2\ZZ$-graded, and it is invariant for the group $\spin(3;\RR)$.  This twist was identified in work of Geyer-M\"ulsch and of Bak-Gustavsson\cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
\end{itemize}

\textbf{Dimension 4}
\begin{itemize}
 \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.  This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.  It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.  In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.  In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.  Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.  This twist was studied by Johansen \cite{Johansen}.
 \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.  This twist is equivalent to a generalized version of BF theory with two real directions and one complex holomorphic direction, coupled to a generalized version of a $U$-valued symplectic boson.  This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.  This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
 \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.  This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.  Its equations of motion include the Donaldson-Witten equations.  If the supersymmetry is promoted to $\mc N=4$, then this theory is identified either with the theory studied by Vafa and Witten, \cite{VafaWitten}, or with the A-twist studied by Kapustin and Witten \cite{KapustinWitten}, depending on the twisting homomorphism one uses to make the twisted theory $\spin(4;\RR)$-invariant.
 \item \emph{$\mc N=4$ topological B twist.} If $\mc N=4$, there are additional topological twists.  The most important one is the Kapustin-Witten B-twist \cite{KapustinWitten}.  This theory is obtained by dimensional reduction from the B-twist of 5d $\mc N=2$, or by twisting by a special supercharge of rank $(2,2)$.  It is equivalent to a topological BF theory.  This theory is $\spin(4;\RR)$-invariant using the Kapustin-Witten twisting homomorphism, and can be defined on arbitrary 4-manifolds.
 \item \emph{More general $\mc N=4$ topological twists} In the $\mc N=4$ case, the B-twist fits into a larger family of topological twists, most of which are perturbatively trivial.  A $\bb{CP^1}$-family of such twists, generically of rank $(2,2)$, was studied by Kapustin and Witten \cite{KapustinWitten}, which is invariant for $\spin(4;\RR)$ using the Kapustin-Witten twisting homomorphism.  There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.  An analysis of these twists using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
\end{itemize}

@@

\pagestyle{standard}
\part{Supersymmetric Gauge Theory} \label{formalism_part}

@@

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, \omega, S)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, \omega, S)$ is an element 
\[S_\fg = \sum_{k\geq 0} S_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
of cohomological degree zero, where $S_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $S_\fg^{(0)} = S$.
\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $S^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
\item[(c)] $S_\fg$ satisfies the Maurer--Cartan equation:
\[\d_{\mr{CE}} S_\fg + \frac{1}{2} \{S_\fg, S_\fg\} = 0.\]
\end{itemize}
\end{definition}

\begin{remark}
We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $S_\fg$.
Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + \{\fS_\fg, -\}$ 
defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
\[
\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
\]
combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
\end{remark}

@@

\item An action $S_\fg$ of its super Lie algebra $\fg$ with $S^{(k)}_\fg = 0$ for $k\geq 2$ 
\end{itemize}
These are required to satisfy the following conditions:
\begin{itemize}
\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$ and the action functional $S$.

\item For every $x\in\fg$, the vector field $X_{{S^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
\end{itemize}
\end{definition}

@@

Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
\[
S_{\fA} = S + \sum_{k \geq 1} S_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.

\begin{definition} \label{def:twisting}
Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge. The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
\[S^Q = S + \sum_{k \geq 1} S_{\fA}^{(k)}(Q, \dots, Q).\]
\end{definition}

@@

\subsection{Super Yang--Mills Theory: pure gauge theory}
\label{sect:gaugemultipletSUSY}

@@

Evaluating the equation
\[\d_{\mr{CE}} S_{\gauge}^{(2)} + \{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\} = 0\]
on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero. Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $S_{\gauge}^{(2)}$.

>>>>

\section*{Introduction} 
\label{sect:intro}
\addcontentsline{toc}{section}{Introduction}

@@

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

@@

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} Super Yang--Mills theory in 8 dimensions admits three classes of twists.  The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
 \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The holomorphic twist also admits a deformation to a topological twist defined on $\spin(7)$-manifolds. This theory is perturbatively trivial, in the sense that the classical BV complex is contractible. It was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}. The partition function of this theory counts $\spin(7)$-instantons modulo gauge \cite{Lewis,DonaldsonThomas,ReyesCarrion}. If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
\begin{equation} 
 F = \ast (\Omega\wedge F).
 \end{equation}
\end{itemize}

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang--Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.  The minimal twist, by a pure spinor, is equivalent to a generalized version of the BF theory defined on a product of a complex 3-fold and a real 1-manifold.
 \item \emph{$\mc N=1$ intermediate twist.} The minimal twist admits a deformation to a twist by a rank 1 impure spinor. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau surface and a real oriented 3-manifold. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The minimal twist also admits a deformation to a topological twist defined on $G_2$-manifolds. This theory is again perturbatively trivial. It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}. The partition function of this theory counts $G_2$-monopoles modulo gauge \cite{DonaldsonSegal}. If we denote by $\psi$ the calibration 4-form on a $G_2$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying
\begin{equation}
d_A\sigma = \ast(F_A\wedge \psi).
\end{equation}
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model). In general, this theory is only $\ZZ/2\ZZ$-graded. If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/G$. 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$. This twist is also calculated in a forthcoming work of Dylan Butson \cite{Butson}.
 \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists. The one by a supercharge of rank $(2, 2)$ is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau curve and a real oriented 4-manifold. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} The other intermediate twist, by a rank $(1, 1)$ supercharge, is equivalent to a generalized form of the BF theory defined on a product of a complex surface and a real surface.
 \item \emph{$\mc N=(1,1)$ topological twist.} The special rank $(1, 1)$ twist admits a deformation to a topological twist defined on Calabi--Yau 3-folds. This theory is perturbatively trivial. It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}. The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}. If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
\begin{align}
F_{0, 2} + \ol\dd^*_A u &= 0 \\
F_{1, 1}\wedge \omega^2 + [u, \bar{u}] &= 0.
\end{align}
\end{itemize}

\textbf{Dimension 5}
\begin{itemize}
 \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} The minimal twist of 5d $\cN=1$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to a theory defined on a product of a Calabi--Yau surface $X$ and a real 1-manifold $M$. The classical solutions are given by maps from $X\times M$ to the symplectic reduction of $U$ holomorphic along $X$ and locally-constant along $M$. In general, this theory is only $\ZZ/2\ZZ$-graded. It was studied by K\"all\'en and Zabzine \cite{KallenZabzine}. If $U=T^* R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of maps from $X\times M$ to $R/G$ holomorphic along $X$ and locally-constant along $M$. 5d $\cN=2$ super Yang--Mills corresponds to the special case $R=\fg$.
 \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case the minimal twist admits a deformation to an intermediate twist. The corresponding theory is equivalent to a generalized BF theory defined on a product of a complex curve $C$ and a real 3-manifold $M$. The twist was considred in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
 \item \emph{$\mc N=2$ topological A twist.} The intermediate twist admits a deformation to two topological twists. One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1, 1)$ super Yang--Mills theory. This theory is perturbatively trivial. It was studied by Qiu and Zabzine, \cite{QiuZabzine} (see also \cite{Anderson} for a discussion of the twisting homomorphism). The partition function of this theory counts solutions to the Haydys--Witten equations \cite{Haydys,WittenFivebranes}. Let $M$ be a $K$-contact manifold and denote by $R$ the Reeb vector field. The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $B\in\Omega^2(M; \mathrm{ad} P)$ satisfying a self-duality equation $\iota_R \ast B = B$ which together satisfy the following equations (see \cite[equations (4) and (5)]{QiuZabzine}; we refer there for the explanation of the notation):
\begin{align}
\iota_R F - (d_A^* B)^H &= 0 \\
F^+_H - \frac{1}{4}B\times B - \frac{1}{2}\iota_R d_A B &= 0.
\end{align} 
 \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with a 5d Chern--Simons theory defined on an oriented 5-manifold. Note that this theory is only $\ZZ/2\ZZ$-graded. This twist was identified in work of Geyer--M\"ulsch and of Bak--Gustavsson \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
\end{itemize}

\textbf{Dimension 4}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$. This twist was studied by Johansen \cite{Johansen}.
 \item \emph{$\cN=2$ and $\cN=4$ holomorphic twist.} We may also consider holomorphic twists of 4d $\cN=2$ and 4d $\cN=4$ super Yang--Mills theories. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of holomorphic maps from a Calabi--Yau surface $X$ to the Hamiltonian reduction of $U$. 4d $\cN=4$ super Yang--Mills corresponds to the case $U=T^*\fg$ in which case the space of classical solutions is a $(-1)$-shifted cotangent bundle to the moduli stack of $G$-Higgs bundles on a complex surface $X$.
 \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.} There is a deformation of the $\cN=2$ holomorphic twist which is equivalent to a theory of maps from a product of a Calabi--Yau curve $C$ and an oriented surface $\Sigma$ into the Hamiltonian reduction of $U$ which are holomorphic along $C$ and locally-constant along $\Sigma$. This twist was previously studied by Kapustin \cite{KapustinHolo}.
 \item \emph{$\mc N=2$ topological rank (2, 0) twist.} The $\cN=2$ holomorphic twist admits a deformation to a topological twist, the \emph{Donaldson twist}. This theory is perturbatively trivial. This theory was first considered in \cite{WittenTQFT}, and the coupling to matter was studied in \cite{AnselmiFre, AlvarezLabastida, HyunParkPark}. The partition function counts solutions to nonabelian Seiberg--Witten equations \cite{Pidstrigach}. Let $G_\RR$ be a compact Lie group and $U$ a quaternionic-unitary $G_\RR$-representation. In particular, $U$ carries a commuting $\SU(2)$-action given by unit quaternions. Suppose $M$ is a spin 4-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(4)$-principal bundle. The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \SU(2)} U)$ which together satisfy
\begin{align}
\sd \d_A u &= 0 \label{eq:SW1} \\
F^+ + \Phi(u) &= 0, \label{eq:SW2}
\end{align}
where $\Phi$ is the moment map and $\sd\d_A$ is the Dirac operator (we refer to \cite{Pidstrigach,HaydysDirac} for more details).

\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for 4d $\cN=4$ super Yang--Mills, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e. there are three ways of interpreting the differential equations on arbitrary oriented 4-manifolds. First, considering 4d $\cN=4$ super Yang--Mills as a 4d $\cN=2$ super Yang--Mills with $U=\fg\otimes\mathbb{H}$, we obtain a theory which counts solutions to the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}. Another twisting homomorphism was studied by Vafa and Witten \cite{VafaWitten}. The corresponding theory counts solutions of the Vafa--Witten equations on an oriented 4-manifold $M$. The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a self-dual two-form $B\in\Omega^{2, +}(M, \mathrm{ad} P)$ and a section $C\in\Gamma(M, \mathrm{ad} P)$ which satisfy
\begin{align}
-\d_A C + \d_A^* B &= 0 \\
F^+ - \frac{1}{4}B\times B - \frac{1}{2}[C, B] &= 0.
\end{align}
Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus} and Kapustin and Witten \cite{KapustinWitten}. The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
\begin{align}
(F-\phi\wedge \phi)^+ &= 0\\
(\d_A \phi)^- &= 0 \\
\d^*_A \phi &= 0.
\end{align}

 \item \emph{$\mc N=4$ topological B twist.} For 4d $\cN=4$ super Yang--Mills there is a single topological twist which is not perturbatively trivial. It is equivalent to a topological BF theory defined on a 4-manifold (this theory corresponds to the value $t=\pm i$ of the family considered in \cite{KapustinWitten}).

 \item \emph{$\cN=4$ topological rank $(2, 2)$ twist.} The $\cN=4$ topological B twist admits a deformation to a perturbatively trivial theory. The corresponding deformation is parametrized by $s\in\CC^\times$, where $s=1$ is the topological B twist. Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$. The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
\begin{align}
(F-\phi\wedge\phi +t \d_A \phi)^+ &= 0 \\
(F-\phi\wedge\phi -t^{-1}\d_A \phi)^- &= 0 \\
\d^*_A \phi &= 0.
\end{align}

\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge. The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow C\times \Sigma$ together with a connection $A$ and a section $\phi\in\Gamma(C\times \Sigma, \mathrm{ad} P)$ which satisfy
\begin{align}
(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
\d^*_A \phi &= 0.
\end{align}
Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.

An analysis of topological twists of 4d $\cN=4$ super Yang--Mills using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
\end{itemize}

@@

\part{Supersymmetric Gauge Theory} \label{formalism_part}

@@

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, \omega, S)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, \omega, S)$ is an element 
\[\fS_\fg = \sum_{k\geq 0} \fS_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
of cohomological degree zero, where $\fS_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $\fS_\fg^{(0)} = S$.
\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $\fS^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
\item[(c)] $\fS_\fg$ satisfies the Maurer--Cartan equation:
\[\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0.\]
\end{itemize}
\end{definition}

\begin{remark}
We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $\fS_\fg$.
Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + \{\fS_\fg, -\}$ 
defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
\[
\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
\]
combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
\end{remark}

@@

\item An action $\fS_\fg$ of its super Lie algebra $\fg$ with $\fS^{(k)}_\fg = 0$ for $k\geq 2$ 
\end{itemize}
These are required to satisfy the following conditions:
\begin{itemize}
\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$ and the action functional $S$.

\item For every $x\in\fg$, the vector field $X_{{\fS^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
\end{itemize}
\end{definition}

@@

Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.

\begin{definition} \label{def:twisting}
Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge. The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
\end{definition}

@@

\subsection{Pure Super Yang--Mills Theory}
\label{sect:gaugemultipletSUSY}

@@

Evaluating the equation
\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero. Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
